% LaTeX source of my resume
% =========================
% Commented for easy reuse… ;)
% See the `README.md` file for more info.
% This file is licensed under the CC-NC-ND Creative Commons license.

% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=18mm]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{packages/resume}

% This code block makes it possible to process each line as #1 by defining \doline#1{#1}

% Is there a way to resize // // to \vspace{0.5em}?

\newenvironment{dolines}
	{\begingroup\obeylines\getlines}%
  	{\endgroup}

\def\marker
	{\end{dolines}}
	{\obeylines

\gdef\getlines#1
	{\def\text{#1}%
  		\ifx\text\marker \let\next\text
    	\else
    	\doline{#1}\let\next\getlines \fi
  	\next}}
\def\doline#1{#1\par}

% Makes Scottish lastname commands available.
\usepackage{packages/scottish}



\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins

% \section*{Name and Address Block}

% title on top of the document
\maintitle{Philip \Mc Gaw} {}{} % {June 12, 1982}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph

\noindent\href{mailto:philip@mcgaw.eu}{philip@mcgaw.eu}\sbull
\textsmaller{+}44 7969 502 077\sbull
\href{https://github.com/philipmcgaw}{github.com/philipmcgaw}\sbull
\href{http://linkedin.com/in/philipmcgaw}{linkedin.com/in/philipmcgaw}\sbull
Banbury.

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\section*{Summary}
\vspace{-1.3em}  % some vertical spacing
\input{cv/summary}

\spacedhrule{0em}{-0.4em}

\section*{Experience}

\input{cv/experience/energym}
\input{cv/experience/arrival}
\input{cv/experience/jlr}
\input{cv/experience/cass}
\input{cv/experience/squashedfly}

\vspace{-0.2em}
\begin{center}
  \emph{\small Please refer to \href{http://www.linkedin.com/in/philipmcgaw}{Philip's LinkedIn profile} for a more complete list of work experience along with recommendations.}
\end{center}

\spacedhrule{-0.2em}{-0.4em}

\section*{Education}
\input{cv/education/uop}

\spacedhrule{0.5em}{-0.4em}

\section*{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Leading and recruiting teams of software engineers.  Big fan of Agile methodologies, continuous delivery and functional programming.  Enjoys writing Ruby/\nsp Python/\nsp Java/\nsp \CPP~and Haskell.  Solid knowledge of the full web technology stack.  Able to architect \textit{and} implement distributed/\acr{HA} systems.  Strong Linux administration skills (e.g.\ Bash scripting, Apache/\acr{NGINX}, Postgres/My/No\acr{SQL}, ElasticSearch).  Well experienced with virtualization/containerization (Docker/Kubernetes, \acr{KVM}, Xen and several \acr{AWS} solutions) and DevOps (Puppet).  Emacs user.}


\spacedhrule{1.6em}{-0.4em}

\section*{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {art, Buddhism, cryptography, functional programming, Go (board game), history, music (from classical and jazz to Berlin-techno), \acr{NLP}, permaculture, philosophy, rock climbing, startups, travel, typography (e.g.\ graphic design, \LaTeX), \acr{UX}-design and vegan cuisine.}


\end{document}
