% LaTeX source of my resume
% =========================
% Commented for easy reuse... ;)
% See the `README.md` file for more info.
% This file is licensed under the CC-NC-ND Creative Commons license.


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{packages/resume}

% Makes Scottish lastname commands available.
\usepackage{packages/scottish}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins

% \section*{Name and Address Block}

% title on top of the document
\maintitle{Philip \Mc Gaw} {}{} % {June 12, 1982}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph

\noindent\href{mailto:philip@mcgaw.eu}{philip\mbox{}@\mbox{}mcgaw.eu}\sbull
\textsmaller{+}44 7969 502 077\sbull
\href{https://github.com/philipmcgaw}{github.com/philipmcgaw}\sbull
\href{http://linkedin.com/in/philipmcgaw}{linkedin.com/in/philipmcgaw}\sbull
Banbury.

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\section*{Summary}

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent I have over seven years of professional EMC experience on top of my experience with general electrical and electronics engineering, both via formal education and personal projects, I believe the knowledge and skills built up during this time make me the perfect candidate for the role, One of my personal projects is to build an electric go-kart for my two children, this is being designed to be a frame welded from 20mm square box, and MDF sheet, the motors for it are recovered from “Hoverboards”, the control electronics will be bespoke with custom ESCs.
\\
\\
A work-based solution I delivered was involved with the testing of Traction Inverters for EMC and functional testing, the motors they are designed to drive are 100 kW 400 V brushless motors, meaning at full load they can draw up to 400 A peak, this makes it hard to source the required power. The solution I implemented was to use two traction inverters and two traction motors, and couple the motors mechanically together. One motor would be used as an electronic load, and the other would be running in regeneration mode, applying torque and providing about 80\% of the required electrical energy to the first, this meant that the current provided by the external PSUs could be vastly reduced.
\\
\\
I also implemented a standardisation on the Amphenol Industrial PL282 series of connectors for use in testing, this allows test set-ups to be quicker to set up and modify while ensuring safe isolation and containment for operators from HaV.
\\
\\
In my time consulting for Energym, I have already managed to make a number of suggestions that will improve the reliability of their product and reduce failure rates, coupled with design suggestions allow them to supply customers in both the Fitness Studio, and home markets, and implement functionality not seen on their competitor's products.
\\
\\
I am actively working towards professional registration through the IET, with a view to becoming a chartered engineer.
\\
\\
If I were successful in my application to take up this position, I believe I would bring my experience as an Engineer, as well as my ability to come up with unconventional solutions, or at least ask the questions that inspire others to come up with unorthodox solutions.
\end{multicols}


\spacedhrule{0em}{-0.4em}

\section*{Experience}

\headedsection
  {\href{http://cies.breijs.com}{\acr{CIES.BREIJS.COM.}}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Freelance \acr{IT} Consultant}
    {Oct \apo16 -- present}
    {\bodytext{Provides services related to software development, such as:\@ coaching, audits, process improvement, web/cloud architecture, recruitment strategy and tender advise.  Clients:\@ \href{http://www.burst-digital.com/en}{Burst}, \href{https://hoppinger.com}{Hoppiner} \& \href{http://bit4u.nl}{Bit4U}.}}
}

\headedsection
  {\href{http://www.hoppinger.com}{Hoppinger}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Head of Technology}
    {Apr \apo12 -- Oct \apo16}
    {\bodytext{Hoppinger is an open source minded \emph{full-service} internet agency.  In charge of the dev't capacity, reporting directly to managing director and co-founder Marijn Bom.  Drafted and carried out the technical company vision.  Inspired both devs and management to look beyond \acr{PHP}. Grew custom app dev't into a serious revenue segment.  Implemented continuous delivery. Created and taught several in-house courses.  Enacted testing strategy.  Recruited viciously, in part by organizing educational events.  Restructured to fixed team configurations.  Introduced DevOps (Puppet).  Helped to set up the \textit{Customer Support} and \textit{IT ops} dep'ts.  Contributed to the sales pitches for, and in charge of the software architecture for, all technically challenging projects. Involved with many company-wide process improvements.}}
}

\headedsection
  {\href{http://www.hr.nl}{Rotterdam University of Applied Sciences}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Member of the Professional Advisory Board \textnormal{\textit{(till Sep \apo16)}} \& Guest Lecturer}
    {Sep \apo12 -- present}
    {%\bodytext{Introductory lecture on history of software development and open source for 1\textsuperscript{st} year CS students.}
    }
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://www.intellecap.com}{Intellecap}/\href{http://istpl.in}{\acr{ISTPL}}}
  {\textsc{Mumbai, Pune \& Hyderabad, India}} {%

  \headedsubsection  % sets the header for a subsection and contains usually body text
    {\acr{IT} Consultant}
    {Nov \apo08 -- Feb \apo09}
    {\bodytext{Intellecap is a financial advisory firm serving corporates, non-profits and governments working in developing markets. Assessed their software development team and processes. Trained their devs. Architected and built several web apps; one being Mostfit an open source \acr{MIS} for \href{http://en.wikipedia.org/wiki/Microcredit}{microcredit} lenders.}}

  \headedsubsection
    {\acr{IT} \& Strategy Consultant}
    {Jan \apo10 -- Aug \apo11}
    {\bodytext{Called in to solve several technical challenges and develop growth strategies regarding Mostfit.}}

  \headedsubsection
    {CTO}
    {Oct \apo11 -- Feb \apo12}
    {\bodytext{Proudly joined the \acr{C}-family of Intellicap's software division, ISTPL, to make \href{https://github.com/Mostfit/mostfit}{Mostfit} the nr.1 software solution for micro credit lenders around the globe.  Shut down in six months due to lack of investment.}}
}

\headedsection
  {\href{http://www.zarafa.com}{Zarafa}}
  {\textsc{Delft, The Netherlands}} {%
  \headedsubsection
    {\acr{QA} \& Release Manager}
    {Dec \apo09 -- Jan \apo11}
    {\bodytext{Before 2015, when Zarafa entered in an extensive parnership with Amazon, it was probably the fastest growing open source product company in Europe, making a drop-in replacement for MS Exchange.  Reported directly to the \acr{CEO}, Brian Josef, and worked closely with the \acr{CTO}, Steve Hardy.  In charge of the 6 men strong QA dep't.  Established test automation and continuous integration.  Architected and implemented an all-integrated documentation and translation system that employed community effort.  Got sent to India to analyse and streamline their outsourced operations.}}
}

\headedsection
  {\href{http://www.dharmapublishing.com}{Dharma Publishing}}
  {\textsc{near San Francisco, \acr{USA}}} {%
  \headedsubsection
    {\acr{IT} Consultant}
    {Nov \apo09 -- Dec \apo09}
    {\bodytext{Dharma Publishing, the worlds largest Buddhist publisher, is a non-profit, all-volunteer organisation to preserve Tibetan buddhism and culture. Built their web shop, improved related processes.}}
}

\headedsection
  {\href{http://www.kde.org}{KDE}}
  {\href{http://edu.kde.org/kturtle}{edu.kde.org/kturtle}} {%
  \headedsubsection
    {Software Engineer}
    {Dec \apo03 -- present}
    {\bodytext{\acr{KT}urtle is an educational programming environment that simplifies learning the basics of programming.  \acr{KT}urtle is intended as a gift to future generations:\ a simple environment to get started with programming.  In 2003 \acr{KT}urtle got admitted to the \acr{KDE} project.}}
}

\headedsection
  {\href{http://truetopiaproject.org}{Truetopia Project}}
  {\href{http://truetopiaproject.org}{truetopiaproject.org}} {%
  \headedsubsection
    {Initiator \& Lead Developer}
    {Nov \apo07 -- Apr \apo10}
    {\bodytext{The Truetopia Project is an open source web application (Rails) to facilitate self-governing communities.  It provides a workflow for collaborative problem identification and solution design.}}
}

\headedsection
  {\href{http://www.dpu.ac.th/dpuic}{Dhurakij Pundit University International College}}
  {\textsc{Bangkok, Thailand}} {%
  \headedsubsection
    {Guest Lecturer}
    {Sep \apo09}
    {\bodytext{Invited by Dr.\@ Pilun Piyasirivej and Mr.\@ Michel Bauwens to deliver several guest lectures.}}
}

\headedsection
  {\href{http://www.opendream.th}{Opendream}}
  {\textsc{Bangkok, Thailand}} {%
  \headedsubsection
    {Freelance \acr{IT} Consultant}
    {Aug \apo09 -- Sep \apo09}
    {\bodytext{Architected and largely implemented an open source media sharing web service (\acr{REST API}) that facilitates video uploads, transcoding and streaming.  Coached their development team on system design, Ruby web development and software engineering methodologies (Scrum/\acr{TDD}/\acr{BDD}).}}
}

\headedsection
  {\href{http://www.commuun.nl}{Commuun}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Senior Visionary}
    {Jul \apo06 -- Sep \apo09}
    {\bodytext{Set up the technical infrastructure, defined the business cases, created the brand and built several Rails-based web applications with Peter Duijnstee, my close friend and proprietor of Commuun.}}
}

\headedsection
  {\href{http://www.eur.nl}{Erasmus University Rotterdam}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Guest Lecturer}
    {Jul \apo06 -- Jul \apo09}
    {\bodytext{Spoke on the phenomenon of open source on request of Prof.\ Michiel van Wezel.}}
}

%\headedsection
%  {LIP Automatisering}
%  {\textsc{Breda, The Netherlands}} {%
%  \headedsubsection
%    {Software Auditor}
%    {Sep \apo06}
%    {\bodytext{Audited their flag ship product \emph{\acr{LIP} Suite}:\ an %\acr{ERP} solution for construction companies.}}
%}

\headedsection
  {
    \href{http://www.thehealthagency.com}{The Health Agency}
    \acr{(now \href{http://www.minddistrict.com}{MindDistrict})}
  }
  {\textsc{Delft \& Rotterdam, The Netherlands}} {%

  \headedsubsection
    {Software Engineer}
    {Jun \apo05 -- Feb \apo06}
    {\bodytext{Worked on their \acr{CMS} (written in Python and uses Postgre\acr{SQL}, \acr{XML}/\acr{XSLT} and Twisted).}}

  \headedsubsection
    {Software Auditor}
    {Dec \apo06}
    {\bodytext{Assessed their Python/Zope/\acr{Z}o\acr{DB}-based product re-engineering effort.}}
}

\vspace{-0.2em}
\begin{center}
  \emph{\small Please refer to \href{http://www.linkedin.com/in/ciesbreijs}{Cies' LinkedIn profile} for a more complete list of work experience along with recommendations.}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\section*{Education}

\headedsection
  {\href{http://www.eur.nl/english}{Erasmus University Rotterdam}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {BSc in Business Computer Science \textnormal{~(\acr{CS}~\,\&\,Economics)}}
    {2004 -- 2007}
    {\bodytext{Main projects on the economics of open source and the semantic web (\acr{RDF}/\acr{RDFS}, \acr{OWL} \& \acr{SPARQL}).}}
}

\headedsection
  {\href{http://www.tudelft.nl/en}{Technical University Delft}}
  {\textsc{Delft, The Netherlands}} {%
  \headedsubsection
    {Industrial Design Engineering \textnormal{\textit{~(discontinued)}}}
    {2001 -- 2002} {}
}

\headedsection
  {\href{http://www.libanonlyceum.nl}{Libanon Lyceum}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {VWO \textnormal{~(Pre-University Secondary Education)}}
    {1994 -- 2000} {}
}


\spacedhrule{0.5em}{-0.4em}

\section*{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Leading and recruiting teams of software engineers.  Big fan of Agile methodologies, continuous delivery and functional programming.  Enjoys writing Ruby/\nsp Python/\nsp Java/\nsp \CPP~and Haskell.  Solid knowledge of the full web technology stack.  Able to architect \textit{and} implement distributed/\acr{HA} systems.  Strong Linux administration skills (e.g.\ Bash scripting, Apache/\acr{NGINX}, Postgres/My/No\acr{SQL}, ElasticSearch).  Well experienced with virtualization/containerization (Docker/Kubernetes, \acr{KVM}, Xen and several \acr{AWS} solutions) and DevOps (Puppet).  Emacs user.}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {Dutch \emph{(mother tongue)}, English \emph{(full professional proficiency)}, German \emph{(limited working proficiency)}, French \emph{(elementary proficiency)} and Mandarin Chinese \emph{(beginner)}.}


\spacedhrule{1.6em}{-0.4em}

\section*{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {art, Buddhism, cryptography, functional programming, Go (board game), history, music (from classical and jazz to Berlin-techno), \acr{NLP}, permaculture, philosophy, rock climbing, startups, travel, typography (e.g.\ graphic design, \LaTeX), \acr{UX}-design and vegan cuisine.}


\end{document}
