\headedsection
  {ARRIVAL Ltd.}
  {\textsc{Banbury}}
  {%
  \headedsubsection
    {Automotive Component \acr{EMC} Engineer}
    {2020 - 2021}
    {\bodytext{
	
	My role was as the Lead Component EMC Engineer, providing subject specialist support for automotive components for EMC, EMF and EMI compliance, and assessment.
	
	\begin{itemize}
	    \item Specifying testing and standards relevant to the component, working with the ARRIVAL product teams to ensure we aim for compliance.
	    \item Reviewing test plans and test reports prepared by internal and external stakeholders.
	    \item Perform review testing at component and whole vehicle integration level to enable comparison between versions of components.
		\item Perform Schematic, PCB and PCBA review of components to better understand test results and enable the integration of modifications to enable compliance.
		\item Health and Safety, and Risk Assessment review of facilities and procedures.
		\item Writing and maintaining test procedures to ensure regulatory compliance with internal and external standards.
		\item Working as a subject specialist.
	\end{itemize}

Typical EMC and EMF standards used within ARRIVAL are ATDETP0048, ATDETP0049, CISPR 25 Edition 4 (Working towards Edition 5), ICNIRP 1998, 2010 and 2020, UNECE Regulation 10, and GB 8702 2014.
\\
\\
This position required the experience gained while with both CASS and JLR, I have also had the opportunity to pick up new skills.
The project management experience I gained working at JLR has helped me adjust to a more senior position, with more responsibilities.
\\
\\
Project management skills were used in writing the specification, the tendering of the contract and overseeing the construction and setup of a new Conducted Immunity and Emissions facility for testing Battery Electric vehicles, and components, this facility included a 10 meter long SAC, amplifiers, control PCs and software (ETS Lindgren’t Tile and Vision TRX applications) and Receivers.
\\
\\
Until the new laboratory was operational my responsibilities included interfacing with external test houses and service providers in regards to purchasing services based on test plans produced by either myself or the component team. These documents need to convey enough information to allow someone who has never seen the component before to perform testing whilst ensuring a robust EMC sign-off (at component and vehicle level) and ensure that radio reception (customer satisfaction) is not compromised. 
\\
\\
Other duties included:
	\begin{itemize}
	    \item Writing test plans for both full testing and quick evaluation tests.
	    \item Writing test reports for both full testing and quick evaluation tests.
	    \item Working closely with external stakeholders and suppliers.
	    \item Daily maintenance of the test facility and constant improvement of the processes within the test laboratory.
	    \item Ensuring all equipment is calibrated including cables and test equipment.
	    \item Helping clients gain compliance by ensuring the correct standards are used during testing.
	    \item On failure to meet the requirements of EMC, offering advice on cost-effective fixes, ranging from decoupling on the mainboard to correct track and board layout.
	    \item Development of test plans and procedures in line with manufacturing and design requirements.
	    \item Test of complex electronic equipment.
	    \item Evaluation of Technical problems to develop proposals for investigations and corrective actions, including process improvements.
	\end{itemize}
Other parts of my role were:
	\begin{itemize}
	    \item Review schematics, PCB layouts, technical datasheets, simulation results and design calculations. Based on this review I am required to provide design recommendations to engineering teams to meet EMC and EMI requirements, and any other improvements I can derive from the data.
	    \item Ensuring the correct design requirements have been met by the component team.
	    \item provide technical leadership to troubleshoot component and system issues.
	    \item Reviews both schematics and PCBs for EMC best practice
	    \item Perform ECU and PCB level assessments using a variety of test equipment.
	    \item work closely together with component teams developing electronic devices
	    \item communicating complex technical information to all levels of leadership in a clear and concise manner to aid issue resolution.
	    \item Researching new measurement techniques and design custom electronic instrumentation and physical parts to facilitate testing and provide more streamlined stakeholder service.
	\end{itemize}
Where there is a risk of issues on the vehicle, I worked with the Vehicle EMC engineer to perform vehicle level EMC assessments, based on the impact of the issues, either looking for containment or mitigation to meet the requirements of the legal requirements.
\\
\\
While working at Arrival I learned about High power electronics design to support EV system development, this involved working with the Powertrain team and the High Voltage Battery Module team to safely test HaV components and systems.

}}}