\headedsection
  {CASS Industries Ltd.}
  {\textsc{Manchester}}
  {%
  \headedsubsection
    {EMC Test and Compliance Engineer (commercial)}
    {2014 – 2018}
    {\bodytext{
My main duties involved managing the testing of clients' electrical and electronic products for compliance with European Directives and appropriate test standards using RF measurement techniques and electronic test equipment such as Oscilloscopes, and Spectrum Analysers.
Other duties included:
	\begin{itemize}
	    \item Writing test reports for both full testing and quick evaluation tests.
	    \item Daily maintenance of the test facility and constant improvement of the processes within the test laboratory.
	    \item Ensuring all equipment was calibrated including cables and test equipment.
	    \item Helping clients gain compliance by ensuring the correct standards are used during testing.
	    \item On failure to meet the requirements of EMC, offering advice on cost-effective fixes, ranging from decoupling on the mainboard to correct track and board layout.
	    \item Developing test plans and procedures in line with manufacturing and design requirements.
	    \item Testing of complex electronic equipment.
	    \item Evaluating Technical problems to develop proposals for investigations and corrective actions, including process improvements.
	    \item Looking after the internal network, desktop computers, and servers (Microsoft Office on Windows 7 and 10).
	\end{itemize}
I also assisted with researching new measurement techniques, designing custom electronic instrumentation and physical parts to facilitate testing and provide more streamlined customer service.
\\
\\
Typical EMC standards used within the test facility would be EN55032, EN50130-4, and the EN61000 series of standards.
}}}