\headedsection
  {Jaguar Land Rover.}
  {\textsc{Gaydon}}
  {%
  \headedsubsection
    {Automotive Component \acr{EMC} Engineer}
    {2018 - 2020}
    {\bodytext{
	
	Working with a team of Engineers and Technical Specialists on several cross vehicle line projects and, technical projects including EMF investigation.
	\\
	\\
	My role as project manager included, clearly and concisely providing subject specialist support for around 60 automotive components for EMC compliance and assessment.
	
	\begin{itemize}
	    \item Specifying testing and standards relevant to the component, working with the JLR component managers to ensure compliance.
	    \item Reviewing test plans and test reports prepared by internal and external stakeholders.
	    \item Perform review testing at component and whole vehicle integration level to enable comparison between versions of components.
		\item Perform Schematic, PCB and PCBA review of components to better understand test results and enable the integration of modifications to enable compliance.
		\item Health and Safety, and Risk Assessment review of facilities and procedures.
		\item Writing and maintaining test procedures to ensure regulatory compliance with internal and external standards.
		\item Working as a subject specialist.
		\item Author of the tender document for a new two lab EMC facility to replace the current one from the 1980s.
	\end{itemize}

	Typical EMC and EMF standards used within JLR are JLR-EMC-CS, CISPR 25 Edition 3, ICNIRP 1998 and 2010, UNECE Regulation 10, and GB 8702 2014.

}}}