\headedsection
  {Squashed Fly Ltd.}
  {\textsc{}}
  {%
  \headedsubsection
    {Freelance Geek}
    {2006 – 2014}
    {\bodytext{
Website design and hosting for some clients, including pro-bono work for charities. SquashedFly’s servers are Debian and Ubuntu Linux, managed via SSH, sites being built using WordPress as a CMS.
\\
\\
Several long and short terms IT contracts covering First, Second and Third Tier support, Dev Ops and Administration roles, for companies and organisations including:

	\begin{itemize}
	    \item McCann Erickson.
	    \item Secure Borders and Communities (SERCO).
	    \item UK Borders Agency.
	    \item Allegro Networks.
	    \item FACT (Foundation for Art and Creative Technology).
	    \item Pennant Training Systems Ltd.
	    \item Department for Work and Pension.
	    \item Ministry of Justice.
	    \item Freedom Press.
	    \item BIMM Institute (British and Irish Modern Music Institute).
	\end{itemize}
Experience:
	\begin{itemize}
	    \item Supporting and managing IT estates of more than 500 Windows 7 and Mac OS X users, in high-pressure production environments.
	    \item DBS checked, Working within the Official Secrets Act, and International Traffic in Arms Regulations, Holding Security Vetting.
	    \item Munki!, Jamf and Deploy Studio
	    \item Lone and out of hours working.
	    \item Day to day running of the IT and Technical resources.
	    \item Ensuring Service Level Agreements (SLAs) are met at all times.
	    \item Deploying bare metal images to Mac and Windows computers.
	    \item Maintenance of Linux servers (LAMP stack and email)
	    \item Hosting and maintaining the security of WordPress installs.
	\end{itemize}
}}}